### 2014-03-01 thesis/src/chapters/chapter-adaptivity.tex
Thesis: adaptivity fix

\chapter{Problem domain}
\chapterintro{This chapter details mechanisms and practises that ensures a requested Quality-of-Service level is met by a means of a self-adaptive system that scales across multiple service providers.}

@@

\subsection{Introduction}
Guaranteeing Quality-of-Service, a critical concept in this paper, can be seen as continuous monitoring and reacting to undesirable conditions when necessary. In fact, this process is as an IT procedure and traditionally belongs to the duties of a system administrator. Figure \ref{fig:it-process} illustrates exemplary IT procedure.

@@

While system administrator can be directly responsible for manually performing steps depicted in figure \ref{fig:it-process}, it is much more favourable to automatize this process leading to a self-manageable system. Not only does it lead to efficiency of an IT process but also to its effectiveness \cite{IBM06} achieved through:
\begin{itemize}
  \item \emph{rapid process initiation} - components auto-initiates actions based on information derived from a system
  \item \emph{reduced time and skill requirements} - automatization of IT processes makes them easier and less troublesome what is especially important for skill-intensive, error-prone and long lasting tasks
\end{itemize}

@@

What control loop is made of is collection of data, its analysis, making a decisions and enforcing them in the environment. Figure \ref{fig:feedback-loop} depicts a generic feedback loop, giving context associated with each phase.

@@

Successive sections details aforementioned phases and gives an examples of systems leveraging feedback loops.

>>>>

\chapter{Problem domain}
\chapterintro{This chapter details mechanisms and practises that ensures a Quality-of-Service level is met by means of a self-adaptive system that scales across multiple service providers.}

@@

\subsection{Introduction}
Guaranteeing Quality-of-Service can be seen as continuous monitoring and reacting to undesirable conditions when necessary. In fact, this process is an IT procedure performed by system administrator. Figure \ref{fig:it-process} illustrates an example of such procedure. While system administrator can be directly responsible for manually performing steps depicted in figure \ref{fig:it-process}, it is much more favourable to automatize this process leading to a self-manageable system. Not only does it lead to efficiency of an IT process but also to its effectiveness \cite{IBM06}. It is achieved through:
\begin{itemize}
  \item \emph{rapid process initiation} - components auto-initiate actions based on information derived from a system
  \item \emph{reduced time and skill requirements} - automatization of IT processes makes them easier and less troublesome what is especially important for skill-intensive, error-prone and long lasting tasks
\end{itemize}

@@

@@

What control loop is made of is:
\begin{inparaenum}[1)]
 \item collection of data
 \item data analysis
 \item making a decisions
 \item enforcing actions
\end{inparaenum}
Figure \ref{fig:feedback-loop} depicts a generic feedback loop, giving context associated with each phase. Successive sections details aforementioned phases.

@@

### 2014-03-01 thesis/src/chapters/chapter-introduction.tex
Thesis: adaptivity fix

\section{Contributions}
The main contributions of this dissertation are as follows:
\begin{itemize}
  \item A proposal of an architecture of a cloud computing federation, which is based on and can be viewed as a simplified version of \emph{InterCloud}
  \item The implementation of the proposed architecture using OpenNebula technology stack
  \item The evaluation of implemented proof-of-concept
\end{itemize}

\section{Impact}
We hope that the concept of self-adaptation at each level of cloud can be thought-provoking for computing scientists.  What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. 
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be assured:
\begin{itemize}
  \item implementing auto-scaling capabilities
  \item designing \emph{cloud infrastructure} in accordance with InterCloud architecture
\end{itemize}

\section{Thesis structure}

>>>>

\section{Contributions}
The main contributions of this dissertation are as follows:
\begin{itemize}
  \item A proposal of an architecture of a self-adaptive platform that ensures satisfying Quality of Service requirements of deployed users' applications in a cloud computing environment by leveraging horizontal, vertical and cloud-federation-aware scaling
  \item The implementation of the proposed architecture using OpenNebula technology stack
  \item The evaluation of the implemented proof-of-concept system
\end{itemize}

\section{Impact}
We hope that the concept of self-adaptation at each level of cloud can be thought-provoking for computing scientists.  What is more, we believe that our successful attempt to implement the proposed architecture will cause a greater gain in interest in models that enable scaling applications across different cloud providers, e.g. \emph{InterCloud}.
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be assured:

\begin{itemize}
  \item implementing auto-scaling capabilities
  \item designing cloud-federation-aware cloud infrastructures
\end{itemize}

\section{Thesis structure}
This dissertation is organised as follows:

\begin{enumerate}[\bfseries {Chapter} I]
    \setcounter{enumi}{1}
  \item presents an introduction to the problem domain giving an outline and definition of concepts of \emph{self-adaptive systems}, \emph{application scaling} and \emph{interoperability of clouds}
  \item describes and compares similar solutions in the field with the emphasis on their auto-scaling capabilities
  \item presents our proposal of an architecture, giving an in depth description of each component which constitutes it
  \item is devoted to our proof-of-concept implementation of the architecture
  \item provides information regarding tests of the implementation and their results
  \item presents conclusions and points further research directions
\end{enumerate}
